---
title: "08 data Scientist 08"
author: "Gianandrea La Porta"
date: "5/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ggplot2

The grammar of graphic
Download the Cheatsheet at this [link](https://rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf)

```{r}
library(tidyverse)
data("airquality")
airq <- as_tibble(airquality)
```

Questions:

1. What do you want the computer to do?
2. What must the computer know in order to do that?

3 main components for ggplot:

1. data (that you want to visualize)
2. aesthetic mappings (describing how variables in the data are mapped)
3. at least one layer (`geom_*`) which describes how to render each observation (points, lines, polygons, etc.) 

```{r}
ggplot(data = airq, # data
       mapping = aes(x=Wind, y=Temp))+ # aesthetic mappings
  geom_point() # layer
```

```{r}
ggplot(data = airq,
       mapping = aes(x=Wind, y=Temp))+ # copy+paste
  geom_density2d() # different layer
```

```{r}
ggplot(data = airq,
       mapping = aes(x=Wind, y=Temp))+
  geom_point(aes(color=Month>6))+
  labs(title = 'Data air quality', # add a new layer always with +
       subtitle = 'Year 1973',
       x='Wind (mph)', y='Temperature (°F)',
       tag='a)', caption = 'sorce: National ...')
```

`?labs()`

other aesthetics like:
- color
- shape
- size

#### Challenge #1

Create a scatterplot demand~time, with point size = 6 and points colored 
in green and put the source name 'BOD dataset' in the caption.

```{r solution 1 error}
BOD
ggplot(BOD,aes(x=Time,y=demand))+
  geom_point(aes(col='green',size=6))+ # inside aes()
  labs(caption = 'source: BOD dataset')
```

```{r solution 1}
ggplot(BOD,aes(x=Time,y=demand))+
  geom_point(col='green',size=6)+ # outside aes()
  labs(caption = 'source: BOD dataset')
```

If an aesthetic is linked to data it is put into `aes()`, while
if you simply want to set it to a value, put it outside of `aes()`


### geom_smooth()

```{r}
ggplot(data = airq,
       mapping = aes(x=Wind, y=Temp))+
  geom_point()+
  geom_smooth() # loess curve
```

### Challenge #2

Modify the code to make the points larger squares (size=6) and add 
a dashed `geom_smooth` curve.
See `?geom_point` and `?geom_smooth` for more information on the point layer 

```{r solution 2}
ggplot(data = airq,
       mapping = aes(x=Wind, y=Temp))+
  geom_point()+
  geom_smooth() # loess curve
```

hint: linetype is controlled by 'linetype'
hint: remember the difference between mapping and set aesthetics

```{r}
ggplot(data = airq,
       mapping = aes(x=Wind, y=Temp))+
  geom_point(size=6, shape='square', alpha=0.7)+
  geom_smooth(linetype='dashed') # loess curve
```

geoms are drawn in the order they are added.

```{r}
ggplot(data = airq,
       mapping = aes(x=Wind, y=Temp))+
  geom_smooth(linetype='dashed')+ # loess curve
  geom_point(size=6, shape='square', alpha=0.7)
```

```{r}
ggplot(data = airq,
       mapping = aes(x=Wind, y=Temp))+
  geom_smooth(method='lm', col='white',
                linetype='dashed')+ # loess curve
  geom_point(size=6, shape='square', alpha=0.7)
```

### Challenge #3

BOD 
Create a barplot using the `geom_col` and color the bars according to the variable `Time`.

```{r}
ggplot(data=BOD,
       mapping = aes(x=Time,y=demand))+
  geom_col(fill=as.factor(BOD$Time))
```

```{r solution 3}
ggplot(data=BOD,
       mapping = aes(x=Time,y=demand))+
  geom_col(aes(fill=Time))+
  geom_text(aes(label=demand),
            col='white',
            nudge_y = -0.7)
```

```{r}
ggplot(data=BOD,
       mapping = aes(x=Time,y=demand))+
  geom_col(aes(fill=Time))+
  geom_text(aes(label=demand),
            col='white',
            nudge_y = -1.7)+
  coord_polar()
```

### Scales

Scale defines how the mapping you specify inside `aes()` should happen. 

```{r}
ggplot(airq)+
  geom_point(aes(x=Temp, y=Wind, color=Temp))
```

- scale_color_*
- scale_fill_*
- scale_shape_*
- scale_size_*

```{r}
ggplot(airq)+
  geom_point(aes(x=Temp, y=Wind, color=Temp))+
  scale_color_gradient(low = 'blue',
                       high = 'red',
                       name = '°F')
```

```{r}
ggplot(airq)+
  geom_point(aes(x=Temp, y=Wind, color=Temp))+
  scale_color_gradient(low = 'blue',
                       high = 'red',
                       name = '°F')+
  scale_x_continuous(breaks = c(60,80,95))+
  scale_y_continuous(trans= 'log10')
```

#### Challenge #4

Load data from `storms` dataset. The data includes the positions and attributes of 198 tropical storms.
Create a bubble chart (scatterplot with size mapped to a continuous variable) showing:

- `category` maps size and color, 
- `status` maps shape 
- and `x=pressure` and `y=wind`.

```{r solution 4}
data("storms")
ggplot(storms, mapping = aes(x=pressure, y=wind))+
  geom_point(aes(size=category, color=category, shape=status),
             alpha=0.5)
```

#### Palettes
`RColorBrewer()`

```{r}
RColorBrewer::display.brewer.all()
```

```{r}
library(RColorBrewer)
data("storms")
ggplot(storms, mapping = aes(x=pressure, y=wind))+
  geom_point(aes(size=category, color=category, shape=status),
             alpha=0.5)+
  scale_color_brewer(palette = 'BuPu')
```

### Theme

Theming defines the feel and look of your final plot.

```{r}
ggplot(airq, aes(x=Temp, y=Wind))+
  geom_point(size=5, col='yellowgreen')+
  geom_point()+
  labs(title='Air quality')+
  theme_linedraw(base_size = 18,
                 base_family = 'Times New Roman')
```

Install new themes from ggthemes

```{r}
# install.packages('ggtheme')
ggplot(airq, aes(x=Temp, y=Wind))+
  geom_point(size=5, col='white')+
  geom_point()+
  labs(title='Air quality')+
  ggthemes::theme_economist(base_size = 14)
```

### Facetting

Faceting creates tables of graphics by splitting the data into subsets and displaying 
the same graph for each subset.

```{r}
ggplot(airq, aes(x=Temp, y=Wind))+
  geom_point(size=5, col='white')+
  geom_point()+
  facet_wrap(~Month)
```

### ggplot2 and tidyverse packages

ggplot2 works perfectly together with the other tidyverse packages, so pipe data directly
into the ggplot call.

Test
dataset = storms
filter data -- month>6, month<10
plot(x=wind, y=pressure)
facet_grid with month~status


```{r}
storms %>% 
  filter(month>6,month<10) %>% 
  ggplot(aes(x=wind, y=pressure))+
  geom_point(aes(col=pressure))+
  facet_grid(month~status)
```

Explore other geometries...
`geom_boxplot()`
`geom_jitter()`

Check the website [ggplot2](https://ggplot2.tidyverse.org/reference/index.html) for more info
and in addition I strongly recommend everybody to read this book authored by H. Wickham 
"ggplot2: Elegant Graphics for Data Analysis" at https://ggplot2-book.org


